Beyond the Numbers: Dissecting New York City's Leading Causes of Death Across Demographics

### 2024-03-16 paper/paper.qmd
Update paper, clean up redundant files

>>>>

## Model Results

For each population we built a negative binomial and possion regression the model and then use posterior predictive checks to compare the models. We also compare between the models using the resampling method leave-one-out (LOO) cross-validation (CV). The results for the models based on each population is as follows:

### White Non-Hispanic Population

Posterior Predictive Check: 
```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| label: fig-ppcheckpoissonvsbinomial-white
#| layout-ncol: 2
#| fig-cap: "Comparing posterior prediction checks for Poisson and negative binomial models in Leading cause of death of White Non-Hispanic Population in New York City"
#| fig-subcap: ["Negative binomial model", "Poisson model"]

library(magick)

# Load the images
image1 <- image_read("../data/analysis_data/Model_Output/pp_check_neg_binom_white.png")
image2 <- image_read("../data/analysis_data/Model_Output/pp_check_poisson_white.png")

image1
image2
```

Leave-one-out (LOO) cross-validation (CV):

| Model                                    | elpd_diff | se_diff |
|------------------------------------------|-----------|---------|
| Negative Binomial                        | -43.4     | 4.0     |
| Poisson                                  | 0.0       | 0.0     |

### Black Non Hispanic Population 
Posterior Predictive Check: 
```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| label: fig-ppcheckpoissonvsbinomial-black
#| layout-ncol: 2
#| fig-cap: "Comparing posterior prediction checks for Poisson and negative binomial models in Leading cause of death of Black Non-Hispanic Population "
#| fig-subcap: ["Negative binomial model", "Poisson model"]

library(magick)

# Load the images
image1 <- image_read("../data/analysis_data/Model_Output/pp_check_neg_binom_black.png")
image2 <- image_read("../data/analysis_data/Model_Output/pp_check_poisson_black.png")

image1
image2
```

Leave-one-out (LOO) cross-validation (CV):

| Model                                    | elpd_diff | se_diff |
|------------------------------------------|-----------|---------|
| Negative Binomial                        | -37.6     | 3.0     |
| Poisson                                  | 0.0       | 0.0     |

### Hispanic Population

Posterior Predictive Check: 
```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| label: fig-ppcheckpoissonvsbinomial-hispanic
#| layout-ncol: 2
#| fig-cap: "Comparing posterior prediction checks for Poisson and negative binomial models in Leading cause of death of Hispanic Population in New York City"
#| fig-subcap: ["Negative binomial model", "Poisson model"]

library(magick)

# Load the images
image1 <- image_read("../data/analysis_data/Model_Output/pp_check_neg_binom_hispanic.png")
image2 <- image_read("../data/analysis_data/Model_Output/pp_check_poisson_hispanic.png")

image1
image2
```

Leave-one-out (LOO) cross-validation (CV):

| Model                                    | elpd_diff | se_diff |
|------------------------------------------|-----------|---------|
| Negative Binomial                        | -34.0     | 2.8     |
| Poisson                                  | 0.0       | 0.0     |

### Asian And Pacific Islanders Population

Posterior Predictive Check: 
```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| label: fig-ppcheckpoissonvsbinomial-asian
#| layout-ncol: 2
#| fig-cap: "Comparing posterior prediction checks for Poisson and negative binomial models in Leading cause of death of Asian And Pacific Islanders Population in New York City"
#| fig-subcap: ["Negative binomial model", "Poisson model"]

library(magick)

# Load the images
image1 <- image_read("../data/analysis_data/Model_Output/pp_check_neg_binom_asian.png")
image2 <- image_read("../data/analysis_data/Model_Output/pp_check_poisson_asian.png")

image1
image2
```

Leave-one-out (LOO) cross-validation (CV):

| Model                                    | elpd_diff | se_diff |
|------------------------------------------|-----------|---------|
| Negative Binomial                        | -25.7     | 1.4     |
| Poisson                                  | 0.0       | 0.0     |
